Continous time Markov chain models; \\ extension, simulation and visualisation

### 2014-11-20 frontback/summary.tex
typo, B-W moore figure

The {\bussname} simulation software package is discussed in Chapter~\ref{chap:pibuss}, along with a simulation study that aims at exploring the limits of estimating old divergence times when faced with molecular data coming from rapidly evolving viruses.
This study has sparked my interest in developing more biologically realistic codon models, which allow for both across-site and across-branch variation
Such models should improve the resolution with which we can estimate old divergence dates. % especially obscured with purifying selection.
This ongoing work is described in Section~\ref{sub:dpp}.
Future extensions of the {\bussname} simulator are described in Section~\ref{sec:buss_future} and a gentle tutorial on using this software can be found in Appendix~\ref{app:pibuss_tuto}.

>>>>

The {\bussname} simulation software package is discussed in Chapter~\ref{chap:pibuss}, along with a simulation study that aims at exploring the limits of estimating old divergence times when faced with molecular data coming from rapidly evolving viruses.
This study has sparked my interest in developing more biologically realistic codon models, which allow for both across-site and across-branch variation.
Such models should improve the resolution with which we can estimate old divergence dates. % especially obscured with purifying selection.
This ongoing work is described in Section~\ref{sub:dpp}.
Future extensions of the {\bussname} simulator are described in Section~\ref{sec:buss_future} and a gentle tutorial on using this software can be found in Appendix~\ref{app:pibuss_tuto}.
